Outline

### 2017-07-21 Outline.Rmd
Update Outline.Rmd

###Target Journal: 
[*Technology Innovations in Statistics Education*](http://escholarship.org/uc/uclastat_cts_tise)

###Authors (in no particular order)
+ Shannon Pileggi (mailto:spileggi@calpoly.edu), Assistant Professor, Statistics Department, Cal Poly SLO
+ Tessa McDonnel (mailto:tessamcdonnel@ymail.com), Undergraduate Research Assistant, Statistics Department, Cal Poly SLO
+ Weston Stearns??? (mailto:weston@datacamp.com), Lead Community Course Development, DataCamp
+ Mine Centikaya-Rundel??? (mailto:mine@stat.duke.edu) Assistant Professor?, Statistics Department, Duke

###Scope:
(3) Technology Innovations - discussions of new technology created by the author(s)

>>>>

### Target Journal: 
[*Technology Innovations in Statistics Education*](http://escholarship.org/uc/uclastat_cts_tise)

### Authors (in no particular order)
+ Shannon Pileggi (mailto:spileggi@calpoly.edu), Assistant Professor, Statistics Department, Cal Poly SLO
+ Tessa McDonnel (mailto:tessamcdonnel@ymail.com), Undergraduate Research Assistant, Statistics Department, Cal Poly SLO
+ Weston Stearns??? (mailto:weston@datacamp.com), Lead Community Course Development, DataCamp
+ Mine Centikaya-Rundel??? (mailto:mine@stat.duke.edu) Assistant Professor?, Statistics Department, Duke

### Scope:
(3) Technology Innovations - discussions of new technology created by the author(s)
